---
title: "Germination Data Collection"
author: "Omar E. Benites Alfaro"
date: "6/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rfbapp)
```

## Germination variables

Usually in agronomic studies, there exists the necessity of how the germination process of certain plant or variety works. It usually involves consecutives evaluations in time of a germination variable. Flavio et. al (2019) provides a germination study that includes germination evaluations that we are going to mimic to recreate an entire example of how  an `rfbapp` along with `Field Book App`, a mobile phone application, can integrate each other to collect data into the field. 

## Creation of variables

In aforementioned study, there is one variable named `D`, which denote the number of germinated seeds in a certain day. For example: `D1` number of germination seeds at `day 1`. The study especify the number of seeds initially planted are 50 per experimental unit (EU). Thus, the researcher should count how many seed successfully germinated in a certain day from the initial sample of 50 seeds. For example: in day 1, the number of germinated seeds are `D1=39`in first EU. 

To create a variable list in `rfbapp`` that satisfy the aim of our study, we identify the followig attributes:

- variable type: `quantitative`
- minimun number of seeds: `0`
- maximum number of seeds: `50`
- variable name: `D`
- number of evaluations in time: `10`

In `rfbapp` we can create quantitative variables as follows:

```{r}
vars <- create_fbapp_template(variable = "D", type = "numeric", details = "Numer of germinated seeds", ntime = 10)
vars
```
Now we export these set of variables via:

```{r, eval=FALSE}
rfbapp::write_rfbapp(vars,file = "germination_variables.trt")
```








